---
title: "Assignment 1"
author: "Isaac Bragna"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
```

# Exercise 1

## Create a vector of three elements (2,4,6) and name that vector vec_a. Create a second vector, vec_b, that contains (8,10,12). Add these two vectors together and name the result vec_c.

```{r}
vec_a <- c(2,4,6)
vec_b <- c(8,10,12)
vec_c <- vec_a + vec_b
vec_c
```

# Exercise 2

## Create a vector, named vec_d, that contains only two elements (14,20). Add this vector to vec_a. What is the result and what do you think R did? What is the warning message that R gives you?

```{r}
vec_d <- c(14,20)
vec_a + vec_d
```
The result is a vector (16,24,20), which adds the 1st entries together as well as the 2nd entries. However, R provides a warning that the longer object length (3) is not a multiple of shorter object length (2), and it recycles the shorter vector to add the 14 to the 6. The warning messages makes me think something different may have happened if the longer vector was a multiple of the shorter one.
```{r}
vec_a2 <- c(2,4,6,8)
vec_a2 + vec_d
```
Interestingly it recycles in the same fashion without a warning message.

# Exercise 3

## Next add 5 to the vector vec_a. What is the result and what did R do? Why doesn’t in give you a warning message similar to what you saw in the previous problem?

```{r}
vec_a + 5
```
R simply added the number 5 to each factor of vec_a. There is no warning message because the length of vector a is a multiple of the length of the vector containing just 5.

# Exercise 5

## Generate the vector of even numbers {2,4,6,...20}
### a) Using the seq() function

```{r}
seq(2, 20, 2)
```
### Using the a:b shortcut and some subsequent algebra

```{r}
vector <- 1:10
vector*2
```

# Exercise 6

## Generate a vector of 21 elements that are evenly placed between 0 and 1 using the seq() command and name this vector x.

```{r}
x <- seq(0,1, length.out=21)
x
```

# Exercise 8

## Generate the vector {2,2,2,2,4,4,4,4,8,8,8,8} using the rep() command.

```{r}
rep( c(2,4,8), each=4)
```

# Exercise 11

## Create a data.frame named my.trees that has the following columns:
### Girth = {8.3, 8.6, 8.8, 10.5, 10.7, 10.8, 11.0}
### Height= {70, 65, 63, 72, 81, 83, 66}
### Volume= {10.3, 10.3, 10.2, 16.4, 18.8, 19.7, 15.6}

```{r}
my.trees <- data.frame( Girth = c(8.3,8.6,8.8,10.5,10.7,10.8, 11.0),
                        Height = c(70,65,63,72,81,83,66),
                        Volume = c(10.3,10.3,10.2,16.4,18.8,19.7,15.6))
```

## Extract the third observation (i.e. the third row)

```{r}
my.trees[3,]
```

## Extract the Girth column referring to it by name

```{r}
my.trees['Girth']
```

## Print out a data frame of all the observations except for the fourth observation

```{r}
my.trees[-4,]
```

## Use the which() command to create a vector of row indices that have a girth greater than 10. Call that vector index.

```{r}
index <- which(my.trees$Girth > 10)
index
```

## Use the index vector to create a small data set with just the large girth trees

```{r}
large.trees <- my.trees[4:7,]
large.trees
```

## Use the index vector to create a small data set with just the small girth trees.

```{r}
small.trees <- my.trees[1:3,]
small.trees
```

# Exercise 12

## The following code creates a data.frame and then has two different methods for removing the rows with NA values in the column Grade. Explain the difference between the two.
```{r}
df <- data.frame(name= c('Alice','Bob','Charlie','Daniel'),
                 Grade = c(6,8,NA,9))

df[ -which(  is.na(df$Grade) ), ]
df[  which( !is.na(df$Grade) ), ]
```
The first is finding the values in the column 'Grade' that are NA and using that to exclude the index of that value.

The second is finding the values in the column 'Grade that are not NA and including the indexes of those values.

# Exercise 14

## Create a list named my.test with elements
### x = c(4,5,6,7,8,9,10)
### y = c(34,35,41,40,45,47,51)
### slope = 2.82
### p.value = 0.000131

```{r}
my.test <- list(
  x = c(4,5,6,7,8,9,10),
  y = c(34,35,41,40,45,47,51),
  slope = 2.82,
  p.value = 0.000131
)
str(my.test)
```

## Extract the second element in the list

```{r}
my.test[[2]]
my.test[['y']]
```

## Extract the element named p.value from the list

```{r}
my.test['p.value']
my.test[4]
```