---
title: "Assignment 3"
author: "Isaac Bragna"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Exercise 1

**Write a function that calculates the density function of a Uniform continuous variable on the interval (a,b).**

```{r}
duniform <- function(x, a, b){
  density <- case_when(a<x&b>x ~ 1/(b-a),
                       x<a|x>b ~ 0)
  return(density)
}
duniform(1, 2, 8)     # x<a
duniform(11, 6, 15)   # a<x<b
duniform(13, 3, 7)    # b<x
```
**Part B**

```{r}
duniform2 <- function(x, a, b){
  density <- ifelse(a<x&b>x, 1/(b-a), 0)
  return(density)
}
duniform2(c(0,2,4,6), 1, 5)

microbenchmark::microbenchmark( duniform( seq(-4,12,by=.0001), 4, 8), times=100)
microbenchmark::microbenchmark( duniform2( seq(-4,12,by=.0001), 4, 8), times=100)
```

# Exercise 2

**For your duniform() function provide default values of 0 and 1 for the arguments a and b. Demonstrate that your function is appropriately using the given default values by producing a graph of the density without specifying the a or b arguments.**

```{r}
duniform <- function(x, a=0, b=1){
  density <- case_when(a<x&b>x ~ 1/(b-a),
                       x<a|x>b ~ 0)
  return(density)
}
duniform(0.5)
duniform(4)
duniform(11,6,15)
```

# Exercise 3

**Create a function that takes an input vector of numerical values and produces an output vector of the standardized values.**

```{r}
standardize <- function( x ){
  s_dev <- sd(x)
  xbar <- mean(x)
  stdzd <- c()
  for( i in x ){
    z = (i-xbar)/s_dev
    stdzd <- c(stdzd, z)
  }
  return(stdzd)
}
standardize( c(1,2,3,4,5,6))
```

**Apply this function to each numeric column in a data frame**

```{r}
data( 'iris' )

ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Pre-Transformation')

iris.z <- iris %>% mutate( across(where(is.numeric), standardize) )

ggplot(iris.z, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Post-Transformation')
```

# Exercise 4 

```{r}
fizz_buzz <- function(n){
  list <- seq(n)
  FB_list <- NULL
  for( i in list ){
    fate <- case_when( i %% 15 == 0 ~ 'Fizz-Buzz',
                       i %% 5 == 0 ~ 'Buzz',
                       i %% 3 == 0 ~ 'Fizz',
                       .default =as.character(i))
    FB_list <- paste(FB_list, fate, sep=' ')
  }
  return(FB_list)
}
fizz_buzz(25)
```