---
title: "Assignment 4"
author: "Isaac Bragna"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(refinr  )
```

# Exercise 1

**a) This regular expression matches any string that contains the lowercase grouping 'ab'**

```{r}
strings <- c('triathalon', 'slabbed', 'grape', 'balance', 'Abnormal', 'veneration', 'drab', 'laboratory', 'credit', 'funny')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, 'ab') )
```

**b) This regular expression matches any string that contains the lowercase letters 'a' or 'b'**

```{r}
strings <- c('unlawful', 'wing', 'benefit', 'clash', 'impluse', 'bare', 'praise', 'observation', 'court', 'improvement')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '[ab]') )
```

**c) This regular expression matches any string that begins with the lowercase letters 'a' or 'b'**

```{r}
strings <- c('infringe', 'rub', 'bat', 'closed', 'banish', 'freeze', 'anger', 'honorable', 'attractive', 'complete')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '^[ab]') )
```

**d) This regular expression matches any string that contains at least one digit followed by one space then any case letter 'A'/'a'**

```{r}
strings <- c('12 apples', 'San Diego', '7 arrivals', '12:00 AM', 'Sputnik')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s[aA]') )
```

**e) This regularexpression matches any string that contains at least one digit followed by at least zero space then any case letter 'A'/'a'**

```{r}
strings <- c('13Apricots', 'Milwaukee', 'foraging 4', '3:15  aM', 'Apollo 11')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s*[aA]') )
```

**f) This regular expression matches any string that contains zero or more repititions of any character**

```{r}
strings <- c('djksn', '2', '12/25/1996', 'isthmus', 'Shrek the Musical')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '.*') )
```

**g) This regular expression matches any string that starts with 2 alphanumeric characters followed by the letters 'bar'**

```{r}
strings <- c('fubar', 'bartend', 'babarian', 'embark', ' scabbard')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '^\\w{2}bar') )
```

**h) This regular expression matches any string that contains 'foo.bar' OR starts with 2 alphanumeric characters followed by the letters 'bar'**

```{r}
strings <- c('embark', 'fubar', 'foobar', 'pfoo.barr', 'foo.bar')

data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '(foo\\.bar)|(^\\w{2}bar)') )
```

# Exercise 2

**Produce a data frame with columns corresponding to the site, plot, camera, year, month, day, hour, minute, and second for these three file names**

```{r}
file.names <- c( 'S123.P2.C10_20120621_213422.jpg',
                 'S10.P1.C1_20120622_050148.jpg',
                 'S187.P2.C2_20120702_023501.jpg')

strings <- str_replace_all(file.names, pattern = '\\.', replacement = '_')
strings <- str_split_fixed(strings, pattern = '_', n = 6)

data.frame(strings) %>%
  
  
  
  
  
  
  rename(Site='X1', Plot='X2', Camera='X3', )
```